Appendix A - Alternative DSDM formulations

### 2019-10-16 manuscript/appendix_a.Rmd
patch up presence-only section

We assume presence-only data (where records consist of locations where the species was detected) arise from an a thinned, inhomogenous Poisson point process, as described in [@rennerPointProcessModels2015]. Under this definition, the DSDM relative abundance parameter $\Lambda_i$ represents a density of point observations per unit area (assumed homogenous across each site $i$) that *would* be seen if there were no spatial bias in rates of reporting. The expected number of presence-only observations in a location $i$ is therefore given by the product of the relative abundance $\Lambda_i$, the area $a_i$, and a relative measure of the bias in reporting, $\gamma_i$ (also assumed homogenous across $i$). Values of $\gamma_i$ for each location can be provided as data, or estimated during model-fitting via an additional regression submodel against detection covariates. Since $\Lambda_i$ is only identified to within a multiplicative constant ($\alpha$ in Equation 2), the absolute value of $\gamma_i$ is not identified in this model, so any model for $\gamma_i$ should probably not have an intercept term.

@@

Code:
```{r ppm_obs}
distribution(y) <- poisson(a * gamma * Lambda)
```
Where `y` gives the number of presence-only records reported at site $i$

>>>>

Presence-only data - where records consist of locations where the species has been reported as being present - can be considered as a thinned, inhomogenous Poisson point process [@wartonPoissonPointProcess2010;@rennerPointProcessModels2015]. The likelihood for this model comprises an intractable integral over the study area, which can be approximated in a number of ways that reduce the model to having a Poisson observation model. Here I apply the piecewise constant approximation, defininthe observations $y_i$ to be counts of occurrence records in each cell $i$, having area $a_i$, where the cells represent a partition of the study area [@diggleSpatialSpatioTemporalLogGaussian2013;@simpsonGoingGridComputationally2011]. That is they tesselate (but do not overlap) and together cover the entire study area.
Under this definition, the DSDM relative abundance parameter $\Lambda_i$ represents a density of point observations per unit area (assumed to be homogenous across cell $i$) that *would* be seen if there were no spatial bias in rates of reporting. The expected number of presence-only observations in each cell is therefore the product of the relative abundance $\Lambda_i$, the area $a_i$, and a relative measure of the bias in reporting, $\gamma_i$ (also assumed homogenous across each cell). Values of $\gamma_i$ for each location can be provided as data, or estimated during model-fitting via an additional regression submodel against detection covariates. Since $\Lambda_i$ is only identified to within a multiplicative constant ($\alpha$ in Equation 2), the absolute value of $\gamma_i$ is not identified in this model, so any model for $\gamma_i$ should probably not have an intercept term.

@@

Code:
```{r ppm_obs}
distribution(y) <- poisson(a * gamma * Lambda)
```
Where `y` gives the number of presence-only records reported in cell $i$ and `a` and `gamma` are vectors giving the areas of the cells, and
